\beginsong{Hey Jude}[by=John Lennon]
\beginverse
Hey \[A]Jude, don't make it \[E]bad.
Take a \[E7]sad song and make it b\[A]etter.
Re\[D]member to let her into your he\[A]art,
then you can st\[E]art to \[E7]make it bet\[A]ter.
\endverse
\beginverse
Hey \[A]Jude, don't be afr\[E]aid.
You were \[E7]made to go out and g\[A]et her.
The \[D]minute you let her under your sk\[A]in,
then you beg\[E]in to \[E7]make it be\[A]tter.
\endverse
\beginchorus
\[A7]And anytime you feel the \[D]pain, hey \[F\#m]Jude, ref\[Hm]rain,
don't car\[A]ry the world up\[E7]on your shou\[A]lders.
For \[A7]well you know that it's a \[D]fool who \[F\#m]plays it \[Hm]cool
by ma\[A]king his wo\[E7]rld a little co\[A]lder.
\[A]Da da da \[A7]da \[E7]da...
\endchorus
\beginverse
Hey \[A]Jude, don't let me \[E]down.
You have \[E7]found her, now go and \[A]get her.
Re\[D]member to let her into your \[A]heart,
then you can \[E]start to \[E7]make it bet\[A]ter.
\endverse
\beginchorus
\[A7]So let it out and let it \[D]in, hey \[F\#m]Jude, be\[Hm]gin,
Youre wa\[A]iting for so\[E7]meone to per\[A]form with.
\[A7]And don't you know that it's just \[D]you, hey \[F\#m]Jude, you'll \[Hm]do.
The mo\[A]vement you ne\[E7]ed is on your sho\[A]ulder.
\[A]Da da da \[A7]da \[E7]da...
\endchorus
\beginverse
Hey \[A]Jude, don't make it \[E]bad.
Take a \[E7]sad song and make it b\[A]etter.
Re\[D]member to let her into your he\[A]art,
then you can st\[E]art to \[E7]make it bet\[A]ter.
\endverse
\beginverse*
\[A]Na-na-na, \[G]Na-na-na na, \[D]Na-na-na na, Hey \[A]Jude (10x)
\endverse
\endsong