\beginsong{I See Fire}[by=Ed Sheeran]\beginverse*
If this is to \[Am]end in \[C]fire,
Then we shall \[G]all burn \[Dm]together,
Watch the \[Am]flames climb \[C]higher,
\[G]Into the \[Dm]night.
Calling \[Am]out father\[C] oh,
\[G]Stand by and \[F]we will,
Watch the \[Dm]flames burn \[Em]on and on,
The \[F]mountain\[G]side,
\endverse\beginverse*
And if we should \[Am]die to\[C]night,
We should \[G]all die \[Dm]together.
Raise a \[Am]glass of \[C]wine,
\[G]For the \[Dm]last time.
Calling \[Am]out father \[C]oh,
Pre\[G]pare as we\[F] will,
Watch the \[Dm]flames burn \[Em]on and on,
The \[F]mountain\[G]side.
Des\[Dm]olation \[Em]comes upon the \[F]sky.\[G]
\endverse
\beginchorus
Now I see \[Am]fire,\[F]
\[G]Inside the \[Am]mountain.
I see \[Am]fire,\[F]
\[G]Burning the \[Am]trees.
And I see \[Am]fire,\[F]
\[G]Hollowing \[Am]souls.
I see \[Am]fire,\[F]
\[G]Blood in the \[Dm]breeze.
And I’ll hope that you’ll remember me.
\endchorus\beginverse*
Oh should my \[Am]people \[C]fall then,
Surely \[G]I’ll do \[Dm]the same.
Confined in \[Am]mountain \[C]halls,
We got too \[G]close to the \[Dm]flame.
Calling \[Am]out father \[C]oh,
\[G]Hold fast and we \[F]will,
Watch the \[Dm]flames burn \[Em]on and on,
The \[F]mountain\[G]side.
Des\[Dm]olation \[Em]comes upon the \[F]sky.\[G]
\endverse\beginverse*
And if the \[Dm]night is \[Am]burning,
I will \[C]cover my \[G]eyes,
For if the \[Dm]dark ret\[Am]urns,
Then my \[C]brothers will \[G]die.
And as the \[Dm]sky is falling \[Am]down,
It crashed in\[C]to this lonely \[G]town.
And with that \[Dm]shadow upon the \[C]ground,
I hear my \[F]people screaming \[G]out.
\endverse\beginverse*
And, I see\[Am] fire,\[F]
\[G]Inside the \[Am]mountain.
I see \[Am]fire,\[F]
\[G]Burning the \[Am]trees.
And I see \[Am]fire,\[F]
\[G]Hollowing \[Am]souls.
I see \[Am]fire,\[F]
\[G]Blood in the \[Am]breeze.
I see \[Am]fire,
(Oh you \[F]know I saw a city \[G]burning.)
\[Am]Fire.
And I see \[Am]fire
(Feel the \[F]heat upon my sk\[G]in.)
\[Am]Fire.
And I see \[Am]fire,
oooooo\[F]ooooooooooo\[G]oooohhhhhhhhhhhhh
\[Am]Fire.
And I see \[Am]fire burn o\[F]n and on,
The \[G]mountain\[Am]side.
\endverse\endsong
