\beginsong{Some Nights}[by=Fun.]\beginchorus
\[C]Some nights I stay up ca\[F]shing in my b\[C]ad luck.
\[C]Some nights I call it a \[G]draw.
\[C]Some nights I wish that my li\[F]ps could build a c\[C]astle.
\[F]Some nights I w\[C]ish they'd just fa\[G]ll off
But I s\[F]till wake \[C]up, I still \[F]see your g\[C]host.
Oh Lord, I'm st\[F]ill not su\[C]re what I s\[G]tand for, oh.
\[F]What do I s\[C]tand for? W\[F]hat do I \[C]stand for?
\[F]Most nights, I don't k\[G]now anym\[C]ore\[F]\[C]\[F]\[C]\[G]
\endchorus
\beginverse
\[C]This is it, boys. This is war.
\[F]What are we w\[C]aiting for?
\[F]Why don't we b\[C]reak the rules alr\[G]eady?
I was n\[C]ever one to believe the hype.
\[F]Save that for the bl\[C]ack and white.
I try t\[F]wice as hard and I'm \[C]half as liked,
But h\[G]ere they come again to jack my style
And that's alri\[C]ght
I found a ma\[F]rtyr in my b\[C]ed tonight.
She \[F]stops my bones from w\[C]ondering
Just \[G]who I am, who I am, who I am.
\[C]Yeah, oh \[F]who am \[C]I mm\[F]m m\[G]mmm
\endverse
\beginverse
\[F]Some nights I \[C]wish that this \[F]all would \[C]end
'Cause I\[F] could use some \[C]friends for a cha\[C]nge
And \[F]some nights I'\[C]m scared you'll \[F]forget me \[C]again.
Some \[F]nightis I allways \[C]win (I \[G]allways win)
But I \[F]still \[C]wake up, I still \[F]see your \[C]ghost.
Oh Lord, I \[F]still don't \[C]know what I \[G]stand for, oh.
\[F]What do I \[C]stand for? \[F]What do I \[C]stand for?
\[Am]Most nights, I don't \[G]know
\endverse
\beginverse*
\[F]So this is it? I \[C]sold my soul for this?
\[G]Washed my hands of that for this?
I miss my mom and dad for this?
\[F]No. When I \[C]see stars, that's all they are.
When I \[G]hear songs, they so]und like a swan.
So come o\[F]n. Oh, come \[C]on. Oh, come \[F]on. Oh, come \[G]on!
\endverse\beginverse
\[F]That is it, guys, \[C]that is all.
\[F]Five minutes in and \[C]I'm bored again.
\[F]Ten years of this, and I'm not \[C]sure if any\[G]body understands.
\[F]This is not one for the fol\[C]ks back home.
\[F]I'm sorry to leave, Mom, I \[C]had to go.
\[F]Who the f*** wants to \[C]die alone all \[G]dried up in the desert sun?
\endverse
\beginverse*
My heart is b\[F]reaking for my sister
And the c\[C]on that she called love.
But when I l\[F]ook into my nephew's eyes,
\[F]Man, you wouldn't believe
\[C]The most amazing things that can come f\[G]rom.
Some terrible nig\[C]hts.\[F]\[C]\[F]\[C]\[G]
\endverse
\beginverse*
\[F]The other night, you \[C]wouldn't believe the dre\[F]am I just had \[C]about you and me
\[F]I called you up\[C], but we'd b\[G]oth agree
\[F]It's for the \[C]best you didn't lis\[F]ten
\[F]It's for the \[C]best we get our di\[G]stance.

\endverse\endsong
