\beginsong{Lemon tree}[by=Fool's Garden]
\beginverse
I'm \[Ami]sitting here in a \[Emi]boring room,
It's \[Ami]just another rainy Sunday \[Emi]afternoon.
I'm \[Ami]wasting my time, I got \[Emi]nothing to do.
I'm \[Ami]hanging around, I'm \[Emi]waiting for you,
But \[Dmi]nothing ever happens\[Emi] - and I \[Ami]wonder.\[(Emi)]\[(Ami)]
\endverse
\beginverse
I'm ^driving around ^in my car,
I'm ^driving too fast, I'm ^driving too far.
I'd ^like to change my ^point of view
I ^feel so lonely, I'm ^waiting for you
But ^nothing ever happens^ - and I ^wonder.^ ^
\endverse
\beginchorus
I \[C]wonder how, I \[G]wonder why
\[Ami]Yesterday you told me 'bout the \[Emi]blue blue sky
And \[F]all that I can \[G]see is just a yellow \[C]lemon tree.\[G7]
I'm \[C]turning my head \[G]up and down,
I'm \[Ami]turning turning turning turning \[Emi]turning around
And \[F]all that I can \[G]see is just another \[C]lemon tree.\[G7]
\endchorus
\beginverse*
\[Ami]dab...\[Emi]da da da da \[Ami]di dab dab
\[Emi]da da da da \[Dmi]di dab dab \[Emi]dab didly \[Ami]da!
\endverse
\beginverse
I'm ^sitting here, I ^miss the power.
I'd ^like to go out, take ^in a shower,
But there's a ^heavy cloud in^side my head.
I ^feel so tired, put myself ^into bed,
Where ^nothing ever happens^ - and I ^wonder.^ ^
\endverse
\beginverse*
\[E]Isolation - \[Ami]Is not good for me,
\[G]Isolation - \[C]I don't want to sit on a \[E]lemon tree.
\endverse
\beginverse
I'm ^stepping around in a ^desert of joy
Baby ^anyhow I'll get a^nother toy
And \[Dmi]everything will happen\[Emi] - and you \[Ami]wonder.\[(Emi)] \[(Ami)]
\endverse
\beginchorus \endchorus
\beginchorus
I \[C]wonder how, I \[G]wonder why
\[Ami]Yesterday you told me 'bout the \[Emi]blue blue sky
And \[F]all that I can \[G]see, and \[F]all that I can \[G]see,
And \[F]all that I can \[G]see is just a yellow \[C]lemon tree.
\endchorus
\endsong
