\beginsong{Little talks}[by=Of Monsters and Men]
\beginverse
\[Am]I don't like \[Fmaj7]walking around this \[C]old and empty house
So h\[Am]old my hand, I'll w\[F]alk with you my d\[C]ear
The \[Am]stairs creak \[Fmaj7]as I sleep, it's \[C]keeping me awake
It's the h\[Am]ouse telling y\[F]ou to close your e\[C]yes
\[Am]Some days I \[Fmaj7]can't even \[C]dress myself
It's ki\[Am]lling me to s\[F]ee you this w\[C]ay
\endverse
\beginchorus
'Cause though the \[Am]truth may \[Fmaj7]vary 
This \[C]ship will \[G]carry
Our bo\[Am]dies s\[F]afe to sh\[C]ore
\endchorus
\beginverse
There's an old voice in my head that's holding me back
Tell her that I miss our little talks
Soon it will be over and buried with our past
We used to play outside when we 
were young (and full of life and full of love)
Some days I don't know if I am wrong or right
Your mind is playing tricks on you my dear
\endverse
\beginchorus
'Cause though the \[Am]truth may \[Fmaj7]vary  
This \[C]ship will \[G]carry
Our \[Am]bodies \[Fmaj7]safe to sh\[C]ore  H\[G]ey!
Don't \[Am]listen to a \[Fmaj7]word I \[C]say. \[G]Hey!
The \[Am]screams all \[Fmaj7]sound the \[C]same. \[G]Hey!
'Cause though the \[Am]truth may \[Fmaj7]vary 
This \[C]ship will \[G]carry
Our \[Am]bodies \[Fmaj7]safe to \[C]shore  \[G] 
\endchorus
\beginverse*
You're gone, gone, gone away. I watched you disappear
All that's left is a ghost of you
Now we're torn, torn, torn
apart, there's nothing we can do. 
Just let me go, we'll meet again soon.
Now wait, wait, wait for me. Please hang around
I see you when I fall asleep.
\endverse*
\beginchorus
\lrep Don't listen to a word I say. Hey!
The screams all sound the same. Hey!
'Cause though the truth may vary 
This ship will carry
Our bodies safe to shore\rrep 

'Cause though the \[Am]truth may \[Fmaj7]vary 
This \[C]ship will \[G]carry
Our bo\[Am]dies sa\[F]fe to sh\[C]ore
\endchorus\endsong
